In this experiment, assume that the block length $d$ is fixed.
The goal is to investigate the sparsity level for two types of random dictionaries without and with intra-block orthonormality, and for the six pairs of $q$ and $p$ with tractable operator-norms.

Finally, the sparsity levels for two types of random dictionaries each with six different pairs of $q$ and $p$ are compared to the conventional sparsity levels of Eldar et al. and Donoho and his co-workers.
The result of the experiment is shown in figure \ref{fig:SL_d_Opt_Eldar_Donoho} for (a) $d \seq 2$ and (b) $d \seq 4$.
The first six bars in figure \ref{fig:SL_d_Opt_Eldar_Donoho}(a) and (b) correspond to the proposed sparsity levels for random dictionaries without ($\mySLMath$, orange colour) and with ($SL(\myPhi_{ort})$, blue colour) intra-block orthonormality.
%Remember that for $q \seq p$, the two cases are equal.
Sparsity levels of Donoho et al. for the mentioned two types of dictionary are equal. 
%For the last two bars in figure \ref{fig:SL_d_Opt_Eldar_Donoho}(a) and (b), which correspond to conventional sparsity levels, the notion of the most pessimistic and optimistic is meaningless, so one value is shown.

As it can be seen in figure \ref{fig:SL_d_Opt_Eldar_Donoho}(a) and (b), all the proposed sparsity levels based on Block-MCC$_{q,p}$ for random dictionaries $\myPhi$ without intra-block orthonormality are higher than the conventional sparsity levels introduced by Eldar et al. and Donoho et al. (orange colour), whereas for random dictionaries $\myPhi_{ort}$ with intra-block orthonormality (blue colour), the highest value corresponds to Block-MCC$_{2,2}$, which is equal to the sparsity level of Eldar et al., as proved theoretically in Lemma \ref{lm:Eldar-BMIC} (page \pageref{lm:Eldar-BMIC}), and explained in Remark \ref{Rmrk:Eldar-BMIC-equality}.
%there are three cases in comparison to Eldar's sparsity level.
%For Block-MCC$_{1,1}$ and Block-MCC$_{\infty,\infty}$ the proposed sparsity level is lower than Eldar's, whereas for Block-MCC$_{1,2}$ and Block-MCC$_{2,\infty}$ the proposed sparsity level is higher than Eldar's.
%As explained in Remark \ref{Rmrk:Eldar-BMIC-equality}, for Block-MCC$_{2,2}$ the proposed sparsity level is equal to Eldar's.
At last, all the proposed sparsity levels for two types of dictionaries are higher than the conventional sparsity level of Donoho et al. as proved theoretically in Property \ref{prp:DontKnow1} (page \pageref{prp:DontKnow1}), and explained in Remark \ref{Rmrk:DontKnow1}.
\input{sections/2-4-1-BERC-NumRes-DicOpNorm-Fig6}
\FloatBarrier