\input{sections/5-0-Contributions-ChapTOC}

% ------------------------------------------------------------------------
%\section*{Introduction}
%\addcontentsline{toc}{section}{\protect\numberline{}Introduction}
The contributions of this thesis can be categorized into three main research domains. 
The three classes of research contributions address the three challenges that have been mentioned and discussed in Section Introduction of the dissertation.

In order to explore and address the three mentioned challenges in Introduction, this dissertation is organized in three main parts.
Since the first challenge uses the results of the second challenge, the second challenge is presented in the dissertation before the first challenge, and ultimately in the last part a partial answer to the third challenge is provided through experiments.

First challenge is about the ineffectiveness of some classic methods in high-dimensional problems.
Second challenge raises when classic recovery conditions cannot be established for a new concept of constraint of corresponding optimisation problem, because of materials shortage in new framework. 
Finally, the combination of different information of a same phenomenon is the subject of the third challenge.

In this section, first we briefly recall the challenges and then mention the corresponding contributions to deal with them.

As mentioned in Section Introduction, all the three independent research orientations meet each other in our real-world application, which is distributed EEG/MEG source reconstruction problem, to partially respond to the main research question of the thesis, which is:
\begin{tcolorbox}
%How the diversity of multiple modalities can be effectively exploited in inverse problems with sparsity constraint?
What is the added value of multi-modality, when solving inverse problems?
\end{tcolorbox}
In the following the contributions and perspectives are organized into three sections:
\newpage
% ------------------------------------------------------------------------
\section*{\myhl{High-dimensional problem}}
\input{sections/5-1-Contributions-HighD}
% ------------------------------------------------------------------------
\section*{\myhl{Block-structured problem}}
\input{sections/5-2-Contributions-BStruct}
% ------------------------------------------------------------------------
\section*{\myhl{Multi-modality}}
\input{sections/5-3-Contributions-MultiModality}